On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-03-28 docs/mvfits_paper/mvf.tex
Fix Eq.(20,21) indexing and up claimed order [8]

  \cw_{\lmn} = m/2 + \kappa \sum_{j=1}^{J} c_j \kappa^k \; .

@@

  \cw_{\lmn} = \sum_{j=0}^{J} c_j \kappa^k \; .

@@

In particular, the domain map allows most \qnm{} frequencies to be well modeled by 4th order polynomials which include all lower degree terms; concurrently, the real and imaginary parts of each $\cw\lmn$ are modeled simultaneously.

>>>>

  \cw_{\lmn} = m/2 + \kappa \sum_{j=0}^{J} c_j \kappa^j \; .

@@

  \cw_{\lmn} = \sum_{u=0}^{U} c_u \kappa^u \; .

@@

In particular, the domain map allows most \qnm{} frequencies to be well modeled by 5th order polynomials which include all lower degree terms; concurrently, the real and imaginary parts of each $\cw\lmn$ are modeled simultaneously.
